---
title       : Vehicle Theft Prediction
subtitle    : Developing Data Products
author      : Lee Chun Wai
job         : Coursera Student
logo        : bloomberg_shield.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
url:
    lib: libraries #Remove new if using old slidify
    assets: assets
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
github:
        user : BellyTheMaginificent
        repo : Slidify_Presentation

---

## Chicago Motor Vehicle Theft Analytic

**What is happening**   
1. Vehicle theft cases getting more and more   
2. Number of criminals outnumber the police force   
3. Area of coverage getting bigger as continuous development and expansion on the city landscape.   
   
**Solutions**
> + Crimes is repeatating with certain pattern(s). We could analyze them by time and location information, then using preditive measurment to optimize the police force deployment smartly.

---

## Chicago Motor Vehicle Theft Analytic

Data Loading and basic pre-processing using different __date__ functions
``` {r Library, message=FALSE,echo=FALSE}
library(ggplot2)
library(ggmap)

if(!file.exists(file.path(getwd(), "data")))
{
        dir.create(file.path(getwd(), "data"))
}

src_file = file.path(getwd(), "data/mvt.csv");

if(!file.exists(src_file)){
        url <- "https://github.com/BellyTheMagnificent/Slidify_Presentation/blob/master/Slidify_Presentation/data/mvt.csv"
        download.file(url, src_file, method = "curl")
}

```

``` {r Loading }
mvt = read.csv(src_file, stringsAsFactors=FALSE)
mvt$Date = strptime(mvt$Date, format ="%m/%d/%y %H:%M")
mvt$Weekday = weekdays(mvt$Date)
mvt$Hour = mvt$Date$hour
str(mvt)
```
[Data File](https://github.com/BellyTheMagnificent/Slidify_Presentation/blob/master/Slidify_Presentation/data/mvt.csv) 

---  .class #id 

## Chicago Crime (Weekly)
Most of the theft cases are happen on Friday!
``` {r Weekly, cache=TRUE, echo=FALSE}
WeekdayCounts = as.data.frame(table(mvt$Weekday))
WeekdayCounts$Var1 = factor(WeekdayCounts$Var1, ordered=TRUE, 
                        levels=c("Sunday","Monday","Tuesday", 
                                 "Wednesday","Thursday","Friday","Saturday"))
```

``` {r Weekly_Plot, cache=TRUE, fig.height=4, fig.width=13 }
ggplot(WeekdayCounts, aes (x = Var1, y = Freq)) + geom_line(aes(group=1), alpha=0.3) + 
                 xlab("Days Of the Week ") + ylab("Total Motor Vehicle Thefts")
```

---  .class #id 
   
## Chicago Crime Analytic (Hourly)
From the hourly view of the data, we can conclude that vehicle thefts are active during late night, between 12 am to 1am.
``` {r Hourly, cache=TRUE, echo=FALSE}
DayHourCounts <- as.data.frame(table(mvt$Weekday, mvt$Hour))
DayHourCounts$Var1 = factor(DayHourCounts$Var1, ordered=TRUE, 
                            levels=c("Sunday","Monday","Tuesday", 
                                     "Wednesday","Thursday","Friday","Saturday"))
DayHourCounts$Hour = as.numeric(as.character(DayHourCounts$Var2))
```

``` {r Hourly_Plot, cache=TRUE, fig.width=13, fig.height=4}
ggplot(DayHourCounts,aes(x=Hour,y=Freq,color=Var1,size=1)) + geom_line(aes(group=Var1))
```

---  .class #id 
   
## Chicago Mobile Vehicle Theft (Location)
Visualizing data using Google map do show the are areas which frequently trouble by the theft cases. Perhaps the police department could deploy more forces on this area.
```{r Location, echo=FALSE, message=FALSE, results='hide'}
LatLonCounts = as.data.frame(table(round(mvt$Longitude,2), round(mvt$Latitude, 2)))
LatLonCounts$Long = as.numeric(as.character(LatLonCounts$Var1))
LatLonCounts$Lat = as.numeric(as.character(LatLonCounts$Var2))
LatLonCounts = subset(LatLonCounts, Freq > 0)
chicago = get_map(location = "chicago", zoom = 11)
```
``` {r Slide 2, cache=TRUE, results='hide', message=FALSE, fig.width=13, fig.height=5}
ggmap(chicago) + geom_tile(data=LatLonCounts, aes(x=Long, y=Lat, alpha=Freq), fill="red") + 
         xlab("Longitude") + ylab("Latitude")
```
